%------------------------------------------------------------------------------
\chapter{Acknowledgements}
\label{sec:acknowledgements}
%------------------------------------------------------------------------------
In 2017, I had the fortune to come to Germany and study physics. This would not have been possible without Bonn-Cologne Graduate School, so I would like to thank the admission committee for giving me an opportunity to pursue my master degree in physics.

I would like to thank Prof.\ Dr.\ Ian C.\ Brock for giving me an opportunity to write my thesis in his group. There is no doubt that without his guidance, wisdom and direction over the course of my degree, this thesis would not have been possible. I would also like to thank Prof.\ Dr.\ Florian Bernlochner, who agreed to be my second referee for this thesis.

Furthermore, I would like to thank Prof.\ Dr.\ Heiko Lacker, Dr.\ Janet Dietrich and Ferdinand Schenck from the Berlin VLQ group for helping me to understand the analysis better and also for their fruitful discussions on my results.

A big thanks to Anjishnu Bandyopadhyay for his support right from the beginning, when he introduced me VLQs till the last day of my submission. I truly appreciate all of his efforts for helping me with all my queries irrespective of the time on the clock as well as the priceless discussions on physics-related topics during DPG and at CERN. It has been a pleasure working with him. I would also like to thank Dr.\ Regina Moles Valls and Dr.\ Rui Zhang for their guidance and motivation when I initially joined this group as an intern. I would like to thank Dr.\ Oleh Kivernyk for his valuable suggestions on my results on the ABCD method.

Next, I would like to thank Federico G.\ D.\ Capriles for proofreading my first draft of this thesis and giving me some good memories of card game evenings. I would also like to thank Tanja Holm for the priceless discussions on jets and Christian Kirfel for the general discussions on machine learning related topics as well as teaching me some basic German culture. I would also like to thank Chris Boever for always motivating me and constantly reminding me that I am the next one after him. I am also grateful to him for proofreading some parts of my first draft of this thesis. I would like to thank Hanna We for all the interesting discussions we had on Indian and Korean cultures while sharing the same office. A special thanks to all the other members of the Brock group who were in the group during my days there, including but not limited to Nilima, Nicolas, Piet, Ellinor, Richard.

I would also like to thank everyone in the Desch group for the discussions during the Jamborees. A special thanks to all my friends and colleagues without them, my experience during my degree would not be as enjoyable.

Finally, I would like to thank my parents and family who are \SI{6000}{\kilo\meter} away from me but still their unconditional love and unlimited support encouraged me to start my venture; without them, it would not have been possible for me to manage and finish my studies.


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../mythesis"
%%% End: 
